---
title: "index"
author: "Meishu Zhao"
date: "2024-09-11"
output: html_document
---
**Data**
```{r}
## Install the tidyverse package if you don't have it
if (!require("tidyverse", quietly = TRUE)) {
    install.packages("tidyverse")
}
library("tidyverse")
```

```{r}
## Install the tidytuesdayR package if you don't have it
if (!require("tidytuesdayR", quietly = TRUE)) {
    install.packages("tidytuesdayR")
}

## For the GitHub version of tidytuesdayR (in case the CRAN version is not available)
## you'll need the "remotes" package to install it.
## See for example https://github.com/dslc-io/tidytuesdayR/issues/94 which led
## to tidytuesdayR not been available from CRAN at the end of August 2024

## Install the remotes package if you don't have it
if (!require("remotes", quietly = TRUE)) {
    install.packages("remotes")
}
## Install the tidytuesdayR package (from GitHub) if you don't have it
if (!require("tidytuesdayR", quietly = TRUE)) {
    remotes::install_github("dslc-io/tidytuesdayR")
}
```

```{r}
library("here")
library("tidyverse")

# tests if a directory named "data" exists locally
if (!dir.exists(here("data"))) {
    dir.create(here("data"))
}

# saves data only once (not each time you knit a R Markdown)
if (!file.exists(here("data", "chocolate.RDS"))) {
    url_csv <- "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-18/chocolate.csv"
    chocolate <- readr::read_csv(url_csv)

    # save the file to RDS objects
    saveRDS(chocolate, file = here("data", "chocolate.RDS"))
}
```

```{r}
chocolate <- readRDS(here("data", "chocolate.RDS"))
as_tibble(chocolate)
```
```{r}
glimpse(chocolate)
```

## Part 1
**1. Make a histogram of the rating scores to visualize the overall distribution of scores. Change the number of bins from the default to 10, 15, 20, and 25. Pick on the one that you think looks the best. Explain what the difference is when you change the number of bins and explain why you picked the one you did.**

```{r}
library(ggplot2)

ggplot(chocolate, aes(x = rating)) +
  geom_histogram(bins = 10) +
  ggtitle("Chocolate Rating with 10 bins")

ggplot(chocolate, aes(x = rating)) +
  geom_histogram(bins = 15) +
  ggtitle("Chocolate Rating with 15 bins")

ggplot(chocolate, aes(x = rating)) +
  geom_histogram(bins = 20) +
  ggtitle("Chocolate Rating with 20 bins")

ggplot(chocolate, aes(x = rating)) +
  geom_histogram(bins = 25) +
  ggtitle("Chocolate Rating with 25 bins")
```
I would choose 15 bins. As the number of bins increases, there’s a higher chance that some ratings will have no counts, creating gaps that make it harder to observe the overall trend of the scores. On the other hand, using only 10 bins provides less detail compared to 15, which strikes a good balance between showing enough information and maintaining a clear view of the overall distribution.

**2. Consider the countries where the beans originated from. How many reviews come from each country of bean origin?**
```{r}
chocolate %>%
  count(country_of_bean_origin)
```

**3. What is average rating scores from reviews of chocolate bars that have Ecuador as country_of_bean_origin in this dataset? For this same set of reviews, also calculate (1) the total number of reviews and (2) the standard deviation of the rating scores. Your answer should be a new data frame with these three summary statistics in three columns. Label the name of these columns mean, sd, and total.**
```{r}
chocolate %>%
chocolate[chocolate$country_of_bean_origin=="Ecuador"]
```

**4. Which company (name) makes the best chocolate (or has the highest ratings on average) with beans from Ecuador?**
```{r}

```

**5.Calculate the average rating across all country of origins for beans. Which top 3 countries (for bean origin) have the highest ratings on average?**
```{r}

```

**6. Following up on the previous problem, now remove any countries of bean origins that have less than 10 chocolate bar reviews. Now, which top 3 countries have the highest ratings on average? **
```{r}

```

**7.or this last part, let’s explore the relationship between percent chocolate and ratings.Use the functions in dplyr, tidyr, and lubridate to perform the following steps to the chocolate dataset: Identify the countries of bean origin with at least 50 reviews. Remove reviews from countries are not in this list.Using the variable describing the chocolate percentage for each review, create a new column that groups chocolate percentages into one of four groups: (i) <60%, (ii) >=60 to <70%, (iii) >=70 to <90%, and (iii) >=90% (Hint check out the substr() function in base R and the case_when() function from dplyr – see example below). Using the new column described in #2, re-order the factor levels (if needed) to be starting with the smallest percentage group and increasing to the largest percentage group (Hint check out the fct_relevel() function from forcats).For each country, make a set of four side-by-side boxplots plotting the groups on the x-axis and the ratings on the y-axis. These plots should be faceted by country.On average, which category of chocolate percentage is most highly rated? Do these countries mostly agree or are there disagreements? Hint: You may find the case_when() function useful in this part, which can be used to map values from one variable to different values in a new variable (when used in a mutate() call).**
```{r}
## Generate some random numbers
dat <- tibble(x = rnorm(100))
slice(dat, 1:3)
```

```{r}
## Create a new column that indicates whether the value of 'x' is positive or negative
dat %>%
    mutate(is_positive = case_when(
        x >= 0 ~ "Yes",
        x < 0 ~ "No"
    ))


```











